### 2019-08-09 reports/thesis/chapters/5_inference.tex
Adjustment to thesis
inferenceSubRoi run required experiments
95 percent confidence interval used throughout

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experimental data. The dotted lines shows the 95\% prediction interval.}
  \label{fig:inference_BandwidthSelection2_ruleOfThumb}
\end{figure}

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_subimagePositive.eps}
    \caption{Test statistics}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_densityEstimate.eps}
    \caption{Empirical null fitted onto histogram}
  \end{subfigure}
  \caption{The resulting test statistics are shown in a). The density estimate of the statistics is shown in b). The empirical null distribution multiplied by some constant is also plotted in b); this is to illustrate the curvature is the same as the density estimate at the mode.}
  \label{fig:inference_inferenceSubsampleAll}
\end{figure}

@@

@@

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/fiji/std.png}
        \caption{Standard deviation filter}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/fiji/nullStd.png}
        \caption{Empirical null standard deviation}
    \end{subfigure}
    }
    \caption{Various spread filters with kernel radius $r=5$ on the sample image \texttt{bridge.gif}.}
    \label{fig:inference_fijiStd}
\end{figure}

@@

In this experiment, the empirical null filter was tested to see if it can detect simulated defects from an image with/without contamination. A \emph{defect} is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution. For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.

@@

The main issue with implementing this method onto the production line was how slow the filter was. The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of $\pi r^2$ data points. Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline. On the other hand, the method in \cite{schwartzman2008empirical} which uses the histogram count found that the estimation of the null parameters was insensitive to the histogram binning.

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\mainSize]{../figures/inference/BandwidthSelection2_ruleOfThumb.eps}
  \caption{An identity link gamma GLM was fitted onto the relationship between the optimal bandwidth and $n^{-1/5}$ from the experimental data. The dotted lines shows the 95\% prediction interval.}
  \label{fig:inference_BandwidthSelection2_ruleOfThumb}
\end{figure}

@@

@@

 \begin{figure}[t]
  \centering
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_subimagePositive.eps}
    \caption{Test statistics}
  \end{subfigure}
  \begin{subfigure}[b]{\subSize}
    \includegraphics[width=\textwidth]{../figures/inference/inferenceSubsampleAll_densityEstimate.eps}
    \caption{Empirical null fitted onto histogram}
  \end{subfigure}
  \caption{The resulting test statistics are shown in a). The density estimate of the statistics is shown in b). The empirical null distribution multiplied by some constant is also plotted in b); this is to illustrate the curvature is the same as the density estimate at the mode.}
  \label{fig:inference_inferenceSubsampleAll}
\end{figure}

@@

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/fiji/std.png}
        \caption{Standard deviation filter}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/fiji/nullStd.png}
        \caption{Empirical null standard deviation}
    \end{subfigure}
    }
    \caption{Various dispersion filters with kernel radius $r=5$ on the sample image \texttt{bridge.gif}.}
    \label{fig:inference_fijiStd}
\end{figure}

@@

The empirical null filter was tested to see if it can detect simulated defects from an image with/without contamination. A \emph{defect} is a pixel which has a value not distributed under the null distribution, but instead an alternative distribution. For example suppose $Z_{x,y}|H_{0,x,y}\sim\normal(0,1)$, then a defect would have a value distributed as $Z_{x,y}|H_{1,x,y}\sim\normal(\mu_{1},1)$ where $\mu_1\neq0$.

@@

The main issue with implementing this method onto the production line was how slow the filter was. The main bottleneck is the evaluation of the density estimate, each step in the Newton-Raphson required the evaluation of $\pi r^2$ data points. As a result, increasing the kernel radius slows down the filter. Perhaps there may be faster methods for density estimation such as fitting a smoothing spline on the histogram \citep{efron2004large}, however that would require tuning the histogram bins as well as the tuning parameters for the spline. On the other hand, the method in \cite{schwartzman2008empirical} which uses the histogram count found that the estimation of the null parameters was insensitive to the histogram binning.
